---
title: "Visualisations"
output: html_document
date: "2024-03-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(car)
library(agricolae)
library(Hmisc)
library(GGally)
library(ggcorrplot)
library(gridExtra)
library(patchwork)
library(FSA)
library(rcompanion)
library(ggpubr)
```


## Table reading and preprocessing
```{r}
chains <- read.csv("../GDT/chains_evaluation_filtered_with_gdt.csv", stringsAsFactors = TRUE) |>
  dplyr::select(chain_id, pdb_id, label,
                AF_average_pLDDT, OF_average_pLDDT, EF_average_pLDDT,
                AF_TM_score, OF_TM_score, EF_TM_score,
                AF_RMSD, OF_RMSD, EF_RMSD,
                AF_GDT_TS, OF_GDT_TS, EF_GDT_TS) |>
  drop_na() |>
  setNames(c("chain_id", "pdb_id", "label",
             "AlphaFold2_pLDDT", "OmegaFold_pLDDT", "ESMFold_pLDDT",
             "AlphaFold2_TMscore", "OmegaFold_TMscore", "ESMFold_TMscore",
             "AlphaFold2_RMSD", "OmegaFold_RMSD", "ESMFold_RMSD",
             "AlphaFold2_GDT", "OmegaFold_GDT", "ESMFold_GDT")) 

str(chains)
```

```{r}
chains_longer <- chains |>
  dplyr::select(chain_id, pdb_id, label,
                AlphaFold2_pLDDT, OmegaFold_pLDDT, ESMFold_pLDDT,
                AlphaFold2_TMscore, OmegaFold_TMscore, ESMFold_TMscore,
                AlphaFold2_RMSD, OmegaFold_RMSD, ESMFold_RMSD,
                AlphaFold2_GDT, OmegaFold_GDT, ESMFold_GDT) |>
  pivot_longer(cols = c(AlphaFold2_pLDDT, OmegaFold_pLDDT, ESMFold_pLDDT, AlphaFold2_TMscore, OmegaFold_TMscore, ESMFold_TMscore, AlphaFold2_RMSD, OmegaFold_RMSD, ESMFold_RMSD, AlphaFold2_GDT, OmegaFold_GDT, ESMFold_GDT),
                                        names_to = c("prediction_tool", "metrics"),
                                        names_sep = "_",
                                        values_to = "value") 
str(chains_longer)
```


```{r}
chains_wider <- chains_longer |> 
  pivot_wider(names_from = "metrics", values_from = "value")
str(chains_wider)
```

## Desctiptive statistics
```{r}
summary(chains)
```

```{r}
by(chains, chains$label, summary)
```

```{r}
cbbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

## Average pLDDT
```{r}
letter_sig <- FSA::dunnTest(chains_wider$pLDDT ~ chains_wider$prediction_tool, method="bonferroni")$res
letter_sig <- rcompanion::cldList(P.adj ~ Comparison, data = letter_sig, threshold = 0.05)

plddt <- chains_wider |> 
  ggplot(aes(x = prediction_tool, y = pLDDT, fill = factor(prediction_tool, level = c("AlphaFold2", "ESMFold", "OmegaFold")))) + 
  geom_violin() +
  geom_boxplot(width=0.15, outlier.shape = NA, fill = "white") + 
  scale_fill_manual(values=cbbPalette) +
  labs(x = "prediction tool", y = "average pLDDT") +
  annotate("text", x = c(1, 2, 3), y = tapply(chains_wider$pLDDT, chains_wider$prediction_tool, FUN=function(x) max(x)) + 3, label = letter_sig$Letter) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
plddt
ggsave("plddt.png", width = 15, height = 10, units = "cm")
```

Kruskal-Wallis test:
```{r}
KWtest <- kruskal.test(chains_wider$pLDDT, chains_wider$prediction_tool)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider$pLDDT ~ chains_wider$prediction_tool, method="bonferroni")
dunn
```


## TM score
```{r}
letter_sig <- FSA::dunnTest(chains_wider$TMscore ~ chains_wider$prediction_tool)$res
letter_sig <- rcompanion::cldList(P.adj ~ Comparison, data = letter_sig, threshold = 0.05)

tmscore <- chains_wider |>
  ggplot(aes(x = prediction_tool, y = TMscore, fill = factor(prediction_tool, c("AlphaFold2", "ESMFold", "OmegaFold")))) + 
  geom_violin() +
  geom_boxplot(width=0.1, outlier.shape = NA, fill = "white") + 
  labs(x = "prediction tool", y = "TM score") +
  scale_y_continuous(breaks=c(0, 0.25, 0.5, 0.75, 1)) +
  scale_fill_manual(values=cbbPalette) +
  annotate("text", x = c(1, 2, 3), y = tapply(chains_wider$TMscore, chains_wider$prediction_tool, FUN=function(x) max(x)) + 0.04, label = letter_sig$Letter) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
tmscore
ggsave("tmscore.png", width = 15, height = 10, units = "cm")
```

```{r}
KWtest <- kruskal.test(chains_wider$TMscore, chains_wider$prediction_tool)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider$TMscore ~ chains_wider$prediction_tool, method="bonferroni")
dunn
```


## RMSD
```{r}
letter_sig <- FSA::dunnTest(chains_wider$RMSD ~ chains_wider$prediction_tool)$res
letter_sig <- rcompanion::cldList(P.adj ~ Comparison, data = letter_sig, threshold = 0.05)

rmsd <- chains_wider |>
  ggplot(aes(x = prediction_tool, y = RMSD, fill = factor(prediction_tool, c("AlphaFold2", "ESMFold", "OmegaFold")))) + 
  geom_violin() +
  geom_boxplot(width=0.1, outlier.shape = NA, fill = "white") + 
  ylim(0, 30) +
  labs(x = "prediction tool", y = "RMSD (Å)") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(1.1, 2.1, 3.1), y = c(27, 27, 27), label = letter_sig$Letter) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
rmsd
ggsave("rmsd.png", width = 15, height = 10, units = "cm")
```


```{r}
KWtest <- kruskal.test(chains_wider$RMSD, chains_wider$prediction_tool)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider$RMSD ~ chains_wider$prediction_tool, method="bonferroni")
dunn
```


## GDT-TS
```{r}
letter_sig <- FSA::dunnTest(chains_wider$GDT ~ chains_wider$prediction_tool)$res
letter_sig <- rcompanion::cldList(P.adj ~ Comparison, data = letter_sig, threshold = 0.05)

gdt_ts <- chains_wider |>
  ggplot(aes(x = prediction_tool, y = GDT, fill = factor(prediction_tool, c("AlphaFold2", "ESMFold", "OmegaFold")))) + 
  geom_violin() +
  geom_boxplot(width=0.1, outlier.shape = NA, fill = "white") + 
  labs(x = "prediction tool", y = "GDT-TS") +
  #scale_y_continuous(breaks=c(0, 0.25, 0.5, 0.75, 1)) +
  scale_fill_manual(values=cbbPalette) +
  annotate("text", x = c(1, 2, 3), y = tapply(chains_wider$GDT, chains_wider$prediction_tool, FUN=function(x) max(x)) + 4, label = letter_sig$Letter) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
gdt_ts
ggsave("gdt_ts.png", width = 15, height = 10, units = "cm")
```

```{r}
KWtest <- kruskal.test(chains_wider$GDT, chains_wider$prediction_tool)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider$GDT ~ chains_wider$prediction_tool, method="bonferroni")
dunn
```

```{r}
(plddt | rmsd) / (tmscore | gdt_ts)
ggsave("metrics_grid.png", width = 21, height = 14, units = "cm")
```

## Correlations
### AlphaFold
```{r}
chains_without_outliers <- chains[!(chains$chain_id %in% c("8TVL:A", "8P4Y:A")),]

chains_without_outliers |>
  dplyr::select(AlphaFold2_pLDDT, AlphaFold2_RMSD, AlphaFold2_TMscore, AlphaFold2_GDT) |>
  ggpairs(upper = list(continuous = "points"), lower = list(continuous = "points"), diag = list(continuous = "densityDiag"), columnLabels = c("pLDDT", "RMSD", "TM-score", "GDT-TS")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

#### Pearson's correlation
```{r}
Z <- as.matrix(chains |> dplyr::select(AlphaFold2_GDT, AlphaFold2_TMscore, AlphaFold2_RMSD, AlphaFold2_pLDDT) |> setNames(c("GDT-TS", "TM score", "RMSD", "average\npLDDT")))
R <- rcorr(Z)
diag(R$P) <- 0
alphafold_pearson <- ggcorrplot(R$r, p.mat = R$P, title = "AlphaFold2", 
  lab = TRUE, lab_size = 4.5, lab_col = "white", type = "full", method = "square", outline.color = "white", show.legend = FALSE, pch.cex = 10) + 
  theme(plot.title = element_text(size = 16, hjust = 0.5))
alphafold_pearson
```

#### Spearman correlation
```{r}
R.Sp <- rcorr(Z, type = "spearman")
diag(R.Sp$P) <- 0
alphafold_spearman <- ggcorrplot(R.Sp$r, p.mat = R.Sp$P, title = "AlphaFold2", 
  lab = TRUE, lab_size = 4.5, lab_col = "white", type = "full", method = "square", outline.color = "white", show.legend = FALSE, pch.cex = 10) + 
  theme(plot.title = element_text(size = 16, hjust = 0.5)) 
alphafold_spearman
```

```{r}
R$P
```


### ESMFold
```{r}
chains_without_outliers |>
  dplyr::select(ESMFold_pLDDT, ESMFold_RMSD, ESMFold_TMscore, ESMFold_GDT) |>
  ggpairs(upper = list(continuous = "points"), lower = list(continuous = "points"), diag = list(continuous = "densityDiag"), columnLabels = c("pLDDT", "RMSD", "TM-score", "GDT-TS")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

#### Pearson's correlations
```{r}
Z <- as.matrix(chains |> dplyr::select(ESMFold_GDT, ESMFold_TMscore, ESMFold_RMSD, ESMFold_pLDDT) |> setNames(c("GDT-TS", "TM score", "RMSD", "average\npLDDT")))
R <- rcorr(Z)
diag(R$P) <- 0
esmfold_pearson <- ggcorrplot(R$r, p.mat = R$P, title = "ESMFold", 
  lab = TRUE, lab_size = 4.5, lab_col = "white", type = "full", method = "square", outline.color = "white", show.legend = FALSE, pch.cex = 10) + 
  theme(plot.title = element_text(size = 16, hjust = 0.5))
esmfold_pearson
```

#### Spearman's correlations
```{r}
R.Sp <- rcorr(Z, type = "spearman")
diag(R.Sp$P) <- 0
esmfold_spearman <- ggcorrplot(R.Sp$r, p.mat = R.Sp$P, title = "ESMFold", 
  lab = TRUE, lab_size = 4.5, lab_col = "white", type = "full", method = "square", outline.color = "white", show.legend = FALSE, pch.cex = 10) + 
  theme(plot.title = element_text(size = 16, hjust = 0.5))
esmfold_spearman
```

```{r}
R$P
```


### OmegaFold
```{r}
chains_without_outliers |>
  dplyr::select(OmegaFold_pLDDT, OmegaFold_RMSD, OmegaFold_TMscore, OmegaFold_GDT) |>
  ggpairs(upper = list(continuous = "points"), lower = list(continuous = "points"), diag = list(continuous = "densityDiag"), columnLabels = c("pLDDT", "RMSD", "TM-score", "GDT-TS")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

#### Pearson's correlations
```{r}
Z <- as.matrix(chains |> dplyr::select(OmegaFold_GDT, OmegaFold_TMscore, OmegaFold_RMSD, OmegaFold_pLDDT) |> setNames(c("GDT-TS", "TM score", "RMSD", "average\npLDDT")))
R <- rcorr(Z)
diag(R$P) <- 0
omegafold_pearson <- ggcorrplot(R$r, p.mat = R$P, title = "OmegaFold", legend.title = "Pearson's \ncorrelation \ncoefficient",
  lab = TRUE, lab_size = 4.5, lab_col = "white", type = "full", method = "square", outline.color = "white", pch.cex = 10) +
  theme(legend.title = element_text(size = 12),
        plot.title = element_text(size = 16, hjust = 0.5))
omegafold_pearson
```

#### Spearman's correlations
```{r}
R.Sp <- rcorr(Z, type = "spearman")
diag(R.Sp$P) <- 0
omegafold_spearman <- ggcorrplot(R.Sp$r, p.mat = R.Sp$P, title = "OmegaFold", legend.title = "Spearman's \ncorrelation \ncoefficient",
  lab = TRUE, lab_size = 4.5, lab_col = "white", type = "full", method = "square", outline.color = "white", pch.cex = 10) +
  theme(legend.title = element_text(size = 12),
        plot.title = element_text(size = 16, hjust = 0.5))
omegafold_spearman
```

```{r}
R$P
```


```{r}
alphafold_pearson + esmfold_pearson + omegafold_pearson
ggsave("korelace_pearson.png", height = 3.3, width = 10)
```

```{r}
alphafold_spearman + esmfold_spearman + omegafold_spearman
ggsave("korelace_spearman.png", height = 3.3, width = 10)
```



## Relationship between pLDDT and RMSD, TM-score, and GDT-TS
```{r}
AF_RMSD <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = AlphaFold2_pLDDT, y = AlphaFold2_RMSD), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = AlphaFold2_pLDDT, y = AlphaFold2_RMSD), method = "loess", se = FALSE, color = "brown1") +
  labs(y = "RMSD", x = "average pLDDT", title = "AlphaFold2") +
  ylim(0, 40) + 
  xlim(20, 100) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

AF_RMSD
```

```{r}
AF_TMscore <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = AlphaFold2_pLDDT, y = AlphaFold2_TMscore), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = AlphaFold2_pLDDT, y = AlphaFold2_TMscore), method = "loess", se = FALSE, color = "brown1") +
  labs(y = "TM-score", x = "average pLDDT") +
  ylim(0, 1) +
  xlim(20, 100) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

AF_TMscore
```

```{r}
AF_GDT <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = AlphaFold2_pLDDT, y = AlphaFold2_GDT), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = AlphaFold2_pLDDT, y = AlphaFold2_GDT), method = "loess", se = FALSE, color = "brown1") +
  labs(y = "GDT-TS", x = "average pLDDT") +
  ylim(0, 100) +
  xlim(20, 100) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

AF_GDT
```

```{r}
EF_RMSD <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = ESMFold_pLDDT, y = ESMFold_RMSD), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = ESMFold_pLDDT, y = ESMFold_RMSD), method = "loess", se = FALSE, color = "brown1") +
  labs(y = "RMSD", x = "average pLDDT", title = "ESMFold") +
  xlim(20, 100) +
  ylim(0, 40) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust = 0.5),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

EF_RMSD
```

```{r}
EF_TMscore <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = ESMFold_pLDDT, y = ESMFold_TMscore), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = ESMFold_pLDDT, y = ESMFold_TMscore), method = "loess", se = FALSE, color = "brown1") +
  labs(y = "TM-score", x = "average pLDDT") +
  ylim(0, 1) +
  xlim(20, 100) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

EF_TMscore
```

```{r}
EF_GDT <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = ESMFold_pLDDT, y = ESMFold_GDT), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = ESMFold_pLDDT, y = ESMFold_GDT), method = "loess", se = FALSE, color = "brown1") +
  labs(y = "GDT-TS", x = "average pLDDT") +
  ylim(0, 100) +
  xlim(20, 100) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

EF_GDT
```

```{r}
OF_RMSD <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = OmegaFold_pLDDT, y = OmegaFold_RMSD), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = OmegaFold_pLDDT, y = OmegaFold_RMSD), method = "loess", se = FALSE, color = "brown1") +
  labs(y = "RMSD", x = "average pLDDT", title = "OmegaFold") +
  xlim(20, 100) +
  ylim(0, 40) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust = 0.5),
        axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

OF_RMSD
```

```{r}
OF_TMscore <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = OmegaFold_pLDDT, y = OmegaFold_TMscore), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = OmegaFold_pLDDT, y = OmegaFold_TMscore), method = "loess", se = FALSE, color = "brown1") + 
  labs(y = "TM-score", x = "average pLDDT") +
  ylim(0, 1) +
  xlim(20, 100) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

OF_TMscore
```

```{r}
OF_GDT <- chains_without_outliers |> 
  ggplot() +
  geom_point(aes(x = OmegaFold_pLDDT, y = OmegaFold_GDT), size = 0.6, alpha = 0.2) +
  geom_smooth(aes(x = OmegaFold_pLDDT, y = OmegaFold_GDT), method = "loess", se = FALSE, color = "brown1") + 
  labs(y = "GDT-TS", x = "average pLDDT") +
  ylim(0, 100) +
  xlim(20, 100) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

OF_GDT
```

```{r}
(AF_RMSD | EF_RMSD | OF_RMSD) / (AF_TMscore | EF_TMscore | OF_TMscore) / (AF_GDT | EF_GDT | OF_GDT)
ggsave("scatterplots.png", height = 6.5, width = 10)
```




## Prediction & labels
### Average pLDDT
```{r}
chains_wider_AF <- chains_wider[chains_wider$prediction_tool == "AlphaFold2", ]
KWtest <- kruskal.test(chains_wider_AF$pLDDT, chains_wider_AF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_AF$pLDDT ~ chains_wider_AF$label, method="bonferroni")
dunn
```

```{r}
label_AF_pLDDT <- chains_wider_AF |>
  ggplot(aes(x = prediction_tool, y = pLDDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 103) +
  labs(y = "average\npLDDT", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(103, 3), label = c("a", "a", "a"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(angle = 0, vjust = 0.5),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_AF_pLDDT
```

```{r}
chains_wider_EF <- chains_wider[chains_wider$prediction_tool == "ESMFold", ]
KWtest <- kruskal.test(chains_wider_EF$pLDDT, chains_wider_EF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_EF$pLDDT ~ chains_wider_EF$label, method="bonferroni")
dunn
```

```{r}
label_EF_pLDDT <- chains_wider_EF |>
  ggplot(aes(x = prediction_tool, y = pLDDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 103) +
  labs(y = "average pLDDT", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(103, 3), label = c("a", "a", "a"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_EF_pLDDT
```

```{r}
chains_wider_OF <- chains_wider[chains_wider$prediction_tool == "OmegaFold", ]
KWtest <- kruskal.test(chains_wider_OF$pLDDT, chains_wider_OF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_OF$pLDDT ~ chains_wider_OF$label, method="bonferroni")
dunn
```

```{r}
label_OF_pLDDT <- chains_wider_OF |>
  ggplot(aes(x = prediction_tool, y = pLDDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 103) +
  labs(y = "average pLDDT", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(103, 3), label = c("a", "a", "b"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_OF_pLDDT
```


### TM score
```{r}
KWtest <- kruskal.test(chains_wider_AF$TMscore, chains_wider_AF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_AF$TMscore ~ chains_wider_AF$label, method="bonferroni")
dunn
```

```{r}
label_AF_TMscore <- chains_wider_AF |>
  ggplot(aes(x = prediction_tool, y = TMscore, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 1.05) +
  labs(y = "TM score", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(1.05, 3), label = c("a", "a", "b"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(angle = 0, vjust = 0.5),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_AF_TMscore
```

```{r}
KWtest <- kruskal.test(chains_wider_EF$TMscore, chains_wider_EF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_EF$TMscore ~ chains_wider_EF$label, method="bonferroni")
dunn
```

```{r}
label_EF_TMscore <- chains_wider_EF |>
  ggplot(aes(x = prediction_tool, y = TMscore, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 1.05) +
  labs(y = "TM score", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(1.05, 3), label = c("a", "b", "ab"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_EF_TMscore
```

```{r}
KWtest <- kruskal.test(chains_wider_OF$TMscore, chains_wider_OF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_OF$TMscore ~ chains_wider_OF$label, method="bonferroni")
dunn
```

```{r}
label_OF_TMscore <- chains_wider_OF |>
  ggplot(aes(x = prediction_tool, y = TMscore, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 1.05) +
  labs(y = "TMscore") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(1.05, 3), label = c("a", "a", "a"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_OF_TMscore
```

### RMSD
```{r}
KWtest <- kruskal.test(chains_wider_AF$RMSD, chains_wider_AF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_AF$RMSD ~ chains_wider_AF$label, method="bonferroni")
dunn
```

```{r}
label_AF_RMSD <- chains_wider_AF |>
  ggplot(aes(x = prediction_tool, y = RMSD, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 30) +
  labs(y = "RMSD", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.8, 1.05, 1.3), y = rep(4.5, 3), label = c("a", "a", "a"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(angle = 0, vjust = 0.5),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_AF_RMSD
```

```{r}
KWtest <- kruskal.test(chains_wider_EF$RMSD, chains_wider_EF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_EF$RMSD ~ chains_wider_EF$label, method="bonferroni")
dunn
```

```{r}
label_EF_RMSD <- chains_wider_EF |>
  ggplot(aes(x = prediction_tool, y = RMSD, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 30) +
  labs(x = "prediction tool", y = "RMSD", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.8, 1.05, 1.3), y = c(5.5, 5.5, 3.9), label = c("a", "a", "b"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_EF_RMSD
```

```{r}
KWtest <- kruskal.test(chains_wider_OF$RMSD, chains_wider_OF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_OF$RMSD ~ chains_wider_OF$label, method="bonferroni")
dunn
```

```{r}
label_OF_RMSD <- chains_wider_OF |>
  ggplot(aes(x = prediction_tool, y = RMSD, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 30) +
  labs(y = "TMscore", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.8, 1.05, 1.3), y = c(6.3, 6.3, 4.1), label = c("a", "a", "b"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_OF_RMSD
```

### GDT-TS
```{r}
KWtest <- kruskal.test(chains_wider_AF$GDT, chains_wider_AF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_AF$GDT ~ chains_wider_AF$label, method="bonferroni")
dunn
```

```{r}
label_AF_GDT <- chains_wider_AF |>
  ggplot(aes(x = prediction_tool, y = GDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 104) +
  labs(y = "GDT-TS", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(104, 3), label = c("a", "a", "a"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(angle = 0, vjust = 0.5),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_AF_GDT
```

```{r}
KWtest <- kruskal.test(chains_wider_EF$GDT, chains_wider_EF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_EF$GDT ~ chains_wider_EF$label, method="bonferroni")
dunn
```

```{r}
label_EF_GDT <- chains_wider_EF |>
  ggplot(aes(x = prediction_tool, y = GDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE, outlier.size = 0.8) + 
  ylim(0, 104) +
  labs(y = "GDT-TS", fill = "label") +
  scale_fill_manual(values = cbbPalette) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(104, 3), label = c("a", "b", "a"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_EF_GDT
```

```{r}
KWtest <- kruskal.test(chains_wider_OF$GDT, chains_wider_OF$label)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider_OF$GDT ~ chains_wider_OF$label, method="bonferroni")
dunn
```

```{r}
label_OF_GDT <- chains_wider_OF |>
  ggplot(aes(x = prediction_tool, y = GDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(outlier.size = 0.8) + 
  ylim(0, 104) +
  labs(y = "GDT-TS") +
  scale_fill_manual(
    name = "Label",
    values = cbbPalette,
    labels = c("monomer", "complex", "de novo")
  ) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(104, 3), label = c("a", "a", "a"), size = 3.5) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_OF_GDT
```

```{r}
(label_AF_pLDDT | label_EF_pLDDT | label_OF_pLDDT) / (label_AF_TMscore| label_EF_TMscore | label_OF_TMscore) / (label_AF_RMSD| label_EF_RMSD | label_OF_RMSD) / (label_AF_GDT| label_EF_GDT | label_OF_GDT)
ggsave("labels_grid.png", height = 10, width = 8.5)
```



## Number of better predictions
```{r}
comparison <- rep(c("AlphaFold2 vs. ESMFold", "AlphaFold2 vs. OmegaFold", "ESMFold vs. OmegaFold"), each = 1462)
better_predicted_by <- c(rep(c("AlphaFold2"), 1022), rep(c("ESMFold"), 440), rep(c("AlphaFold2"), 1091), rep(c("OmegaFold"), 371), rep(c("ESMFold"), 869), rep(c("OmegaFold"), 593))

TM_score <- data.frame(comparison, better_predicted_by)

TM_score |> ggplot(aes(x = comparison, fill = better_predicted_by)) + 
    geom_bar(colour = "black", linewidth = 0.3, position = "stack") + 
    labs(x = "prediction tool", y = "number of protein chains") +
    theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```
