---
title: "Visualisations"
output: html_document
date: "2024-03-08"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(car)
library(agricolae)
library(Hmisc)
library(GGally)
library(ggcorrplot)
library(gridExtra)
library(patchwork)
library(FSA)
library(rcompanion)
library(ggpubr)
```


## Table reading and preprocessing
```{r}
chains <- read.csv("chains_evaluation.csv", stringsAsFactors = TRUE) |>
  dplyr::select(chain_id, pdb_id, label, sequence_length, method_of_acquisition,
                AF_average_pLDDT, OF_average_pLDDT, EF_average_pLDDT,
                AF_TM_score, OF_TM_score, EF_TM_score,
                AF_RMSD, OF_RMSD, EF_RMSD,
                AF_vs_OF_RMSD, OF_vs_EF_RMSD, EF_vs_AF_RMSD, AF_vs_OF_TM_score, OF_vs_EF_TM_score, EF_vs_AF_TM_score) |>
  drop_na() |>
  setNames(c("chain_id", "pdb_id", "label", "sequence_length", "method_of_acquisition",
             "AlphaFold2_pLDDT", "OmegaFold_pLDDT", "ESMFold_pLDDT",
             "AlphaFold2_TMscore", "OmegaFold_TMscore", "ESMFold_TMscore",
             "AlphaFold2_RMSD", "OmegaFold_RMSD", "ESMFold_RMSD",
             "AlphaFold2.vs.OmegaFold_RMSD", "OmegaFold.vs.ESMFold_RMSD", "ESMFold.vs.AlphaFold2_RMSD", "AlphaFold2.vs.OmegaFold_TMscore", "OmegaFold.vs.ESMFold_TMscore", "ESMFold.vs.AlphaFold2_TMscore")) 

str(chains)
```

```{r}
chains_longer <- chains |>
  dplyr::select(chain_id, pdb_id, label, sequence_length, method_of_acquisition,
                AlphaFold2_pLDDT, OmegaFold_pLDDT, ESMFold_pLDDT,
                AlphaFold2_TMscore, OmegaFold_TMscore, ESMFold_TMscore,
                AlphaFold2_RMSD, OmegaFold_RMSD, ESMFold_RMSD) |>
  pivot_longer(cols = c(AlphaFold2_pLDDT, OmegaFold_pLDDT, ESMFold_pLDDT, AlphaFold2_TMscore, OmegaFold_TMscore, ESMFold_TMscore, AlphaFold2_RMSD, OmegaFold_RMSD, ESMFold_RMSD),
                                        names_to = c("prediction_tool", "metrics"),
                                        names_sep = "_",
                                        values_to = "value")
str(chains_longer)
```


```{r}
chains_wider <- chains_longer |> 
  pivot_wider(names_from = "metrics", values_from = "value")
str(chains_wider)
```

## Desctiptive statistics
```{r}
summary(chains)
```

```{r}
by(chains, chains$label, summary)
```

```{r}
chains |> ggplot(aes(x = factor(label, level = c("monomer", "complex", "synthetic")), fill = label)) + 
    geom_bar(colour = "black", linewidth = 0.3) + 
    labs(x = "label", y = "number of chains") +
    theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```
```{r}
chains |> ggplot(aes(x = factor(label, level = c("monomer", "complex", "synthetic")), y = sequence_length, fill = label)) + 
    geom_boxplot() + 
    labs(x = "label", y = "length of chain sequence") +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

```{r}
chains |> ggplot(aes(x = factor(label, level = c("monomer", "complex", "synthetic")), fill = method_of_acquisition)) + 
    geom_bar(colour = "black", linewidth = 0.3, position = "stack") + 
    labs(x = "label", y = "number of chains") +
    theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Average pLDDT
```{r}
letter_sig <- FSA::dunnTest(chains_wider$pLDDT ~ chains_wider$prediction_tool, method="bonferroni")$res
letter_sig <- rcompanion::cldList(P.adj ~ Comparison, data = letter_sig, threshold = 0.05)

plddt <- chains_wider |> 
  ggplot(aes(x = prediction_tool, y = pLDDT, fill = factor(prediction_tool, level = c("AlphaFold2", "ESMFold", "OmegaFold")))) + 
  geom_violin() +
  geom_boxplot(width=0.15, outlier.shape = NA, fill = "white") + 
  #scale_fill_viridis(discrete = TRUE) +
  labs(x = "prediction tool", y = "average pLDDT") +
  #stat_compare_means(method = "kruskal.test", label.x = 0.7, label.y = 105) +
  annotate("text", x = c(1, 2, 3), y = tapply(chains_wider$pLDDT, chains_wider$prediction_tool, FUN=function(x) max(x)) + 3, label = letter_sig$Letter) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        #text = element_text(size = 18),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
plddt
ggsave("plddt.png", width = 15, height = 10, units = "cm")
```

Kruskal-Wallis test:
```{r}
KWtest <- kruskal.test(chains_wider$pLDDT, chains_wider$prediction_tool)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider$pLDDT ~ chains_wider$prediction_tool, method="bonferroni")
dunn
```


## TM score
```{r}
letter_sig <- FSA::dunnTest(chains_wider$TMscore ~ chains_wider$prediction_tool)$res
letter_sig <- rcompanion::cldList(P.adj ~ Comparison, data = letter_sig, threshold = 0.05)

tmscore <- chains_wider |>
  ggplot(aes(x = prediction_tool, y = TMscore, fill = factor(prediction_tool, c("AlphaFold2", "ESMFold", "OmegaFold")))) + 
  geom_violin() +
  geom_boxplot(width=0.1, outlier.shape = NA, fill = "white") + 
  labs(x = "prediction tool", y = "TM score") +
  scale_y_continuous(breaks=c(0, 0.25, 0.5, 0.75, 1)) +
  #stat_compare_means(method = "kruskal.test", label.x = 0.7, label.y = 1.07) +
  annotate("text", x = c(1, 2, 3), y = tapply(chains_wider$TMscore, chains_wider$prediction_tool, FUN=function(x) max(x)) + 0.04, label = letter_sig$Letter) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        #text = element_text(size = 18),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
tmscore
ggsave("tmscore.png", width = 15, height = 10, units = "cm")
```

```{r}
KWtest <- kruskal.test(chains_wider$TMscore, chains_wider$prediction_tool)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider$TMscore ~ chains_wider$prediction_tool, method="bonferroni")
dunn
```


## RMSD
```{r}
letter_sig <- FSA::dunnTest(chains_wider$RMSD ~ chains_wider$prediction_tool)$res
letter_sig <- rcompanion::cldList(P.adj ~ Comparison, data = letter_sig, threshold = 0.05)

rmsd <- chains_wider |>
  ggplot(aes(x = prediction_tool, y = RMSD, fill = factor(prediction_tool, c("AlphaFold2", "ESMFold", "OmegaFold")))) + 
  geom_violin() +
  geom_boxplot(width=0.1, outlier.shape = NA, fill = "white") + 
  ylim(0, 30) +
  labs(x = "prediction tool", y = "RMSD (Å)") +
  #stat_compare_means(method = "kruskal.test", label.x = 0.7, label.y = 30) +
  annotate("text", x = c(1.1, 2.1, 3.1), y = c(27, 27, 27), label = letter_sig$Letter) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        #text = element_text(size = 18),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
rmsd
ggsave("rmsd.png", width = 15, height = 10, units = "cm")
```


```{r}
KWtest <- kruskal.test(chains_wider$RMSD, chains_wider$prediction_tool)
KWtest
```

```{r}
dunn <- FSA::dunnTest(chains_wider$RMSD ~ chains_wider$prediction_tool, method="bonferroni")
dunn
```

## Correlations
### AlphaFold
```{r}
chains_without_outliers <- chains[!(chains$chain_id %in% c("8TVL:A", "8P4Y:A", "8B2M:A")),]

chains_without_outliers |>
  dplyr::select(AlphaFold2_pLDDT, AlphaFold2_RMSD, AlphaFold2_TMscore, sequence_length) |>
  ggpairs(upper = list(continuous = "points"), lower = list(continuous = "points"), diag = list(continuous = "densityDiag"), columnLabels = c("pLDDT", "RMSD", "TM-score", "sequence length")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```
#### Pearson's correlation
```{r}
Z <- as.matrix(chains |> dplyr::select(sequence_length, AlphaFold2_TMscore, AlphaFold2_RMSD, AlphaFold2_pLDDT) |> setNames(c("sequence\nlength", "TM score", "RMSD", "pLDDT")))
R <- rcorr(Z)
diag(R$P) <- 0
alphafold_pearson <- ggcorrplot(R$r, p.mat = R$P, title = "AlphaFold", 
  lab = TRUE, lab_size = 5, type = "full", method = "square", outline.color = "white", show.legend = FALSE, pch.cex = 10) + 
  theme(plot.title = element_text(size = 16, hjust = 0.5))
alphafold_pearson
```
#### Spearman correlation
```{r}
R.Sp <- rcorr(Z, type = "spearman")
diag(R.Sp$P) <- 0
alphafold_spearman <- ggcorrplot(R.Sp$r, p.mat = R.Sp$P, title = "AlphaFold", 
  lab = TRUE, lab_size = 5, type = "full", method = "square", outline.color = "white", show.legend = FALSE, pch.cex = 10) + 
  theme(plot.title = element_text(size = 16, hjust = 0.5))
alphafold_spearman
```


### ESMFold
```{r}
chains_without_outliers |>
  dplyr::select(ESMFold_pLDDT, ESMFold_RMSD, ESMFold_TMscore, sequence_length) |>
  ggpairs(upper = list(continuous = "points"), lower = list(continuous = "points"), diag = list(continuous = "densityDiag"), columnLabels = c("pLDDT", "RMSD", "TM-score", "sequence length")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

#### Pearson's correlations
```{r}
Z <- as.matrix(chains |> dplyr::select(sequence_length, ESMFold_TMscore, ESMFold_RMSD, ESMFold_pLDDT) |> setNames(c("sequence\nlength", "TM score", "RMSD", "pLDDT")))
R <- rcorr(Z)
diag(R$P) <- 0
esmfold_pearson <- ggcorrplot(R$r, p.mat = R$P, title = "ESMFold", 
  lab = TRUE, lab_size = 5, type = "full", method = "square", outline.color = "white", show.legend = FALSE, pch.cex = 10) + 
  theme(plot.title = element_text(size = 16, hjust = 0.5))
esmfold_pearson
```
#### Spearman's correlations
```{r}
R.Sp <- rcorr(Z, type = "spearman")
diag(R.Sp$P) <- 0
esmfold_spearman <- ggcorrplot(R.Sp$r, p.mat = R.Sp$P, title = "ESMFold", 
  lab = TRUE, lab_size = 5, type = "full", method = "square", outline.color = "white", show.legend = FALSE, pch.cex = 10) + 
  theme(plot.title = element_text(size = 16, hjust = 0.5))
esmfold_spearman
```


### OmegaFold
```{r}
chains_without_outliers |>
  dplyr::select(OmegaFold_pLDDT, OmegaFold_RMSD, OmegaFold_TMscore, sequence_length) |>
  ggpairs(upper = list(continuous = "points"), lower = list(continuous = "points"), diag = list(continuous = "densityDiag"), columnLabels = c("pLDDT", "RMSD", "TM-score", "sequence length")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

#### Pearson's correlations
```{r}
Z <- as.matrix(chains |> dplyr::select(sequence_length, OmegaFold_TMscore, OmegaFold_RMSD, OmegaFold_pLDDT) |> setNames(c("sequence\nlength", "TM score", "RMSD", "pLDDT")))
R <- rcorr(Z)
diag(R$P) <- 0
omegafold_pearson <- ggcorrplot(R$r, p.mat = R$P, title = "OmegaFold", legend.title = "Pearson's \ncorrelation \ncoefficient",
  lab = TRUE, lab_size = 5, type = "full", method = "square", outline.color = "white", pch.cex = 10) +
  theme(legend.title = element_text(size = 12),
        plot.title = element_text(size = 16, hjust = 0.5))
omegafold_pearson
```

```{r}
R.Sp <- rcorr(Z, type = "spearman")
diag(R.Sp$P) <- 0
omegafold_spearman <- ggcorrplot(R.Sp$r, p.mat = R.Sp$P, title = "OmegaFold", legend.title = "Spearman's \ncorrelation \ncoefficient",
  lab = TRUE, lab_size = 5, type = "full", method = "square", outline.color = "white", pch.cex = 10) +
  theme(legend.title = element_text(size = 12),
        plot.title = element_text(size = 16, hjust = 0.5))
omegafold_spearman
```



```{r}
alphafold_pearson + esmfold_pearson + omegafold_pearson
ggsave("korelace_pearson.png", height = 5.5, width = 16)
```

```{r}
alphafold_spearman + esmfold_spearman + omegafold_spearman
ggsave("korelace_spearman.png", height = 5.5, width = 16)
```


## Prediction & labels
### Average pLDDT
```{r}
chains_wider_AF <- chains_wider[chains_wider$prediction_tool == "AlphaFold2", ]
KWtest <- kruskal.test(chains_wider_AF$pLDDT, chains_wider_AF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_AF$pLDDT ~ chains_wider_AF$label, method="bonferroni")
dunn
```
```{r}
label_AF_pLDDT <- chains_wider_AF |>
  ggplot(aes(x = prediction_tool, y = pLDDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE) + 
  ylim(0, 101) +
  labs(y = "average pLDDT", fill = "label") +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(101, 3), label = c("a", "a", "a")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_AF_pLDDT
```
```{r}
chains_wider_EF <- chains_wider[chains_wider$prediction_tool == "ESMFold", ]
KWtest <- kruskal.test(chains_wider_EF$pLDDT, chains_wider_EF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_EF$pLDDT ~ chains_wider_EF$label, method="bonferroni")
dunn
```

```{r}
label_EF_pLDDT <- chains_wider_EF |>
  ggplot(aes(x = prediction_tool, y = pLDDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE) + 
  ylim(0, 101) +
  labs(y = "average pLDDT", fill = "label") +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(101, 3), label = c("a", "b", "a")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_EF_pLDDT
```

```{r}
chains_wider_OF <- chains_wider[chains_wider$prediction_tool == "OmegaFold", ]
KWtest <- kruskal.test(chains_wider_OF$pLDDT, chains_wider_OF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_OF$pLDDT ~ chains_wider_OF$label, method="bonferroni")
dunn
```

```{r}
label_OF_pLDDT <- chains_wider_OF |>
  ggplot(aes(x = prediction_tool, y = pLDDT, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE) + 
  ylim(0, 101) +
  labs(y = "average pLDDT", fill = "label") +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(101, 3), label = c("a", "b", "c")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_OF_pLDDT
```


### TM score
```{r}
KWtest <- kruskal.test(chains_wider_AF$TMscore, chains_wider_AF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_AF$TMscore ~ chains_wider_AF$label, method="bonferroni")
dunn
```
```{r}
label_AF_TMscore <- chains_wider_AF |>
  ggplot(aes(x = prediction_tool, y = TMscore, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE) + 
  ylim(0, 1.03) +
  labs(y = "TM score", fill = "label") +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(1.03, 3), label = c("a", "a", "b")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_AF_TMscore
```
```{r}
KWtest <- kruskal.test(chains_wider_EF$TMscore, chains_wider_EF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_EF$TMscore ~ chains_wider_EF$label, method="bonferroni")
dunn
```

```{r}
label_EF_TMscore <- chains_wider_EF |>
  ggplot(aes(x = prediction_tool, y = TMscore, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE) + 
  ylim(0, 1.03) +
  labs(y = "TM score", fill = "label") +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(1.03, 3), label = c("a", "b", "a")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_EF_TMscore
```

```{r}
KWtest <- kruskal.test(chains_wider_OF$TMscore, chains_wider_OF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_OF$TMscore ~ chains_wider_OF$label, method="bonferroni")
dunn
```

```{r}
label_OF_TMscore <- chains_wider_OF |>
  ggplot(aes(x = prediction_tool, y = TMscore, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot() + 
  ylim(0, 1.03) +
  labs(y = "TMscore") +
  scale_fill_discrete(name = "Label", labels = c("monomer", "complex", "de novo")) +
  annotate("text", x = c(0.75, 1, 1.25), y = rep(1.03, 3), label = c("a", "b", "a")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_OF_TMscore
```

### RMSD
```{r}
KWtest <- kruskal.test(chains_wider_AF$RMSD, chains_wider_AF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_AF$RMSD ~ chains_wider_AF$label, method="bonferroni")
dunn
```
```{r}
label_AF_RMSD <- chains_wider_AF |>
  ggplot(aes(x = prediction_tool, y = RMSD, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE) + 
  ylim(0, 30) +
  labs(y = "RMSD", fill = "label") +
  annotate("text", x = c(0.8, 1.05, 1.3), y = rep(4.5, 3), label = c("a", "a", "a")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_AF_RMSD
```
```{r}
KWtest <- kruskal.test(chains_wider_EF$RMSD, chains_wider_EF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_EF$RMSD ~ chains_wider_EF$label, method="bonferroni")
dunn
```

```{r}
label_EF_RMSD <- chains_wider_EF |>
  ggplot(aes(x = prediction_tool, y = RMSD, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE) + 
  ylim(0, 30) +
  labs(x = "prediction tool", y = "RMSD", fill = "label") +
  annotate("text", x = c(0.8, 1.05, 1.3), y = c(5.5, 7.5, 3.9), label = c("a", "b", "c")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_EF_RMSD
```

```{r}
KWtest <- kruskal.test(chains_wider_OF$RMSD, chains_wider_OF$label)
KWtest
```
```{r}
dunn <- FSA::dunnTest(chains_wider_OF$RMSD ~ chains_wider_OF$label, method="bonferroni")
dunn
```

```{r}
label_OF_RMSD <- chains_wider_OF |>
  ggplot(aes(x = prediction_tool, y = RMSD, fill = factor(label, level = c("monomer", "complex", "synthetic")))) + 
  geom_boxplot(show.legend = FALSE) + 
  ylim(0, 30) +
  labs(y = "TMscore", fill = "label") +
  annotate("text", x = c(0.8, 1.05, 1.3), y = c(6.3, 7.5, 3.9), label = c("a", "b", "c")) +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())

label_OF_RMSD
```
```{r}
(label_AF_pLDDT | label_EF_pLDDT | label_OF_pLDDT) / (label_AF_TMscore| label_EF_TMscore | label_OF_TMscore) / (label_AF_RMSD| label_EF_RMSD | label_OF_RMSD)
ggsave("labels_grid.png", height = 8.5, width = 8.5)
```


## Method of acquisition
```{r}
chains |> ggplot(aes(x = label, y = AlphaFold2_pLDDT, fill = method_of_acquisition)) + 
  geom_boxplot() + 
  labs(x = "Prediction tool", y = "RMSD", fill = "label") +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```

## Tools between each other
```{r}
chains_longer.between_tools <- chains |>
  dplyr::select(chain_id, pdb_id, label, sequence_length, method_of_acquisition,
                AlphaFold2.vs.OmegaFold_RMSD, OmegaFold.vs.ESMFold_RMSD, ESMFold.vs.AlphaFold2_RMSD,
                AlphaFold2.vs.OmegaFold_TMscore, OmegaFold.vs.ESMFold_TMscore, ESMFold.vs.AlphaFold2_TMscore) |>
  pivot_longer(cols = c(AlphaFold2.vs.OmegaFold_RMSD, OmegaFold.vs.ESMFold_RMSD, ESMFold.vs.AlphaFold2_RMSD,
                        AlphaFold2.vs.OmegaFold_TMscore, OmegaFold.vs.ESMFold_TMscore, ESMFold.vs.AlphaFold2_TMscore),
                                        names_to = c("prediction_tools", "metrics"),
                                        names_sep = "_",
                                        values_to = "value")
str(chains_longer.between_tools)
```

```{r}
chains_wider.between_tools <- chains_longer.between_tools |> 
  pivot_wider(names_from = "metrics", values_from = "value")

str(chains_wider.between_tools)
```

```{r}
RMSD.between_tools <- chains_wider.between_tools |> 
  ggplot(aes(x = prediction_tools, y = RMSD, fill = prediction_tools)) + 
  geom_boxplot() + 
  ylim(0, 30) +
  labs(x = NULL, y = "RMSD", title = "RMSD") +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        text = element_text(size = 18),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
RMSD.between_tools
```
 
```{r}
TMscore.between_tools <- chains_wider.between_tools |> 
  ggplot(aes(x = prediction_tools, y = TMscore, fill = prediction_tools)) + 
  geom_boxplot() + 
  labs(x = NULL, y = "TM score", title = "TMscore") +
  theme(panel.background = element_rect(fill = "white", colour = "black"),
        plot.title = element_text(hjust=0.5),
        legend.position = "none",
        text = element_text(size = 18),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
TMscore.between_tools
```


```{r}
comparison <- rep(c("AlphaFold2 vs. ESMFold", "AlphaFold2 vs. OmegaFold", "ESMFold vs. OmegaFold"), each = 1462)
better_predicted_by <- c(rep(c("AlphaFold2"), 1022), rep(c("ESMFold"), 440), rep(c("AlphaFold2"), 1091), rep(c("OmegaFold"), 371), rep(c("ESMFold"), 869), rep(c("OmegaFold"), 593))

TM_score <- data.frame(comparison, better_predicted_by)

TM_score |> ggplot(aes(x = comparison, fill = better_predicted_by)) + 
    geom_bar(colour = "black", linewidth = 0.3, position = "stack") + 
    labs(x = "prediction tool", y = "number of protein chains") +
    theme(panel.background = element_rect(fill = "white", colour = "black"),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank())
```


















